\documentclass[screen, aspectratio=43]{beamer}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

% Use the NTNU-temaet for beamer 
% \usetheme[style=ntnu|simple|vertical|horizontal, 
%     language=bm|nn|en, 
%     smalltitle, 
%     city=all|trondheim|alesund|gjovik]{ntnu2017}
\usetheme[style=ntnu,language=en]{ntnu2017}

\usepackage[english]{babel}
\usepackage[style=numeric,backend=biber,natbib=false,sorting=none]{biblatex}

\title[HCI-intro]{Human Computer Interaction}
\subtitle{NIMEs (focus on instrument design)}
\author[A. Xamb{\'o}]{Anna Xamb{\'o}}
\institute[NTNU]{Department of Music, NTNU}
\date{1 November 2018}
%\date{} % To have an empty date

\addbibresource{../hci-lectures.bib} % Add bibliography database

% Set the reference style to numeric.
% See here: http://tex.stackexchange.com/questions/68080/beamer-bibliography-icon
\setbeamertemplate{bibliography item}[text] 

% Set bibliography fonts to a small size.
\renewcommand*{\bibfont}{\footnotesize}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

% Alternatively, special title page command to get a different background
% \ntnutitlepage

%
\begin{frame}
\frametitle{Learning Outcomes}
\begin{itemize}
\item Understand the role of a \emph{digital lutherie} or a designer of NIMEs.
\item Explore the key elements of NIME instrument design from an HCI perspective (design \& evaluation).
\item Discern different categories of NIMEs from an HCI design perspective.
\item Be able to create diagrams of self-built NIMEs by reversed engineering methods (learning from existing diagrams).
\end{itemize}
\end{frame}
%
\begin{frame}
\frametitle{Class Structure}
\begin{itemize}
\item 10.15-10.40 Speedy presentations of the short bios.
\item 10.40-11.00 Presentation/lecture about instrument design in NIME from an HCI perspective (design \& evaluation) + Q\&A.
\item 11.00-11.30 Team work: Classification and representation of NIMEs.
\item 11.30-11.50 The teams summarize to the group the results of the team work activity (10 min per group).
\item 11.50-12.00 Wrap up \& Closing
\end{itemize}
\end{frame}
%
\begin{frame}
\frametitle{Preparation: Short Bio}
\begin{itemize}
\item Write a short bio (125 words +/- 10 words) of your hero in music technology. More info can be found on the assignment's page Day 4 Individual Assignment (\url{https://uio.instructure.com/courses/11472/assignments/13452}). Once we discuss all the bios in class, we could publish them as one blog post on the MCT blog! 
\end{itemize}
\end{frame}
%
\begin{frame}
\frametitle{Speedy Presentations: Short Bios}
\end{frame}
%
\begin{frame}
\frametitle{Presentation/lecture: NIME (instrument design)}
\begin{itemize}
\item Presentation/lecture of a selection of concepts in NIME's instrument design from an HCI perspective + Q\&A.
\end{itemize}
\end{frame}
%
\begin{frame}
\frametitle{Team work: Classification and representation of NIMEs}
\begin{itemize}
\item Selection of a paper from the NIME Reader (\url{https://www.springer.com/gp/book/9783319472133}) where a NIME is presented. PDFs can be found in NIME Proceedings (\url{http://www.nime.org/archives/}).
Discussion about ... 
\begin{itemize}
\item what is the type of instrument design presented?
\item how is the instrument design presented in the paper: diagrams? photographs? block diagrams?
 mindmaps?
\end{itemize}
\end{itemize}
\end{frame}
%
\begin{frame}
\frametitle{Team work: Summaries}
\begin{itemize}
\item The teams summarize to the group their selected paper / NIME (10 min per group). 
\begin{itemize}
\item what is the type of instrument design presented?
\item how is the instrument design presented in the paper: diagrams? photographs? block diagrams? mindmaps?
\end{itemize}
\end{itemize}
\end{frame}
%
\begin{frame}
\frametitle{Wrap up \& Closing}
\begin{itemize}
\item From today's examples... how will you represent differently your self-built prototype?
\item Anonymized reviews from the jury members.
\item Drop-in hours under request during the week 5-9 November, 2018.
\item Next WoNoMute: Monday 26 October 2018 14.00--15.00
\item Next Spring: Audio Programming with Web Audio (elective)
\end{itemize}
\end{frame}
%

\begin{frame}
\frametitle{Resources}
\begin{itemize}
\item The content of this class can be found on Canvas here:\\
\url{https://uio.instructure.com/courses/11472/pages/human-computer-interaction-2b}
\item The slides of this class can be found on GitHub here: \\
\url{https://github.com/axambo/hci-lecture-slides/tree/master/slides/d4/}
\item Archive of NIME Proceedings:\\
\url{http://www.nime.org/archives/}
\end{itemize}
\end{frame}
%
%\begin{frame}
%  \frametitle{References}
%  \printbibliography
%\end{frame}
%
\end{document}
